Turbulence in compact to giant HII regions

### 2022-02-01 strucfunc_paper.tex
Finish description of Fig 3 in text

Figure~\ref{fig:velocity-maps} shows maps of the \ha{} centroid velocity
\(V_c\) for each \hii{} region in our sample,
calculated as described above in section~\ref{sec:spectr-datas}
and after subtracting the mean systemic velocity in each case.
The color scheme ranges from the most negative velocities in blue
to the most positive velocities in red,
but the amplitude of the velocity fluctuations differs considerably between regions,
as indicated by the color scale bar on each map,
ranging from \SI{\pm 7}{km.s^{-1}} for the Lagoon
up to  \SI{\pm 40}{km.s^{-1}} for 30~Doradus.
This is illustrated quantitatively in Figure~\ref{fig:hist},
where the probability density function (PDF) of \(V_c\) for each region
is shown on a common velocity scale and arranged in order of decreasing amplitude
of velocity fluctuations. 
All the distributions are far from being consider Gaussian, implying that there are multiple kinematics components in the regions.

>>>>

Figure~\ref{fig:velocity-maps} shows maps of the \ha{} centroid velocity
\(V_c\) for each \hii{} region in our sample,
calculated as described above in section~\ref{sec:spectr-datas}
and after subtracting the mean systemic velocity in each case.
The color scheme ranges from the most negative velocities in blue
to the most positive velocities in red,
but the amplitude of the velocity fluctuations differs considerably between regions,
as indicated by the color scale bar on each map,
ranging from \SI{\pm 7}{km.s^{-1}} for the Lagoon
up to  \SI{\pm 40}{km.s^{-1}} for 30~Doradus.
This is illustrated quantitatively in Figure~\ref{fig:hist},
where the probability density function (PDF) of \(V_c\) for each region
is shown on a common velocity scale and arranged in order of decreasing amplitude
of velocity fluctuations.

All of the distributions are significantly non-Gaussian
and many show evidence of a multi-modal structure.
Some, such as Orion core and Hubble~V, show a single dominant velocity component,
but most show several distinct peaks,
as many as four in the case of Carina.
There is no clear tendency for the number of identifiable velocity components
to increase with increasing velocity dispersion.
Instead, both the widths of the individual peaks and the separation between them
seem to increase in tandem.
For most regions the PDFs are approximately symmetrical,
but two regions show significant skewness:
Orion~core has a smooth asymmetrical tail towards the blue,
whereas NGC~346 has one towards the red.
